Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-03 draft.tex
complete all revisions (prop 2) for homogenized discount factor

Player $p$'s continuation value when the status quo is played for $m-1$ periods before ceding is $0 + \frac{\de_p^m}{1-de_p} \alpha$, whereas the continuation value from war is $\frac{\lambda p_{1s} + \alpha p_{2s}}{1-\de_p} + \frac{\de_p}{1-\de_p}\alpha (1-p_{1s}-p_{2s})$. For player $c$, it is $0 + \frac{\de_p^m}{1-de_p} \beta$ versus $\frac{\nu p_{1s} + \beta p_{2s}}{1-\de_p} + \frac{\de_p}{1-\de_p}\beta (1-p_{1s}-p_{2s})$. Thus the condition for $p$'s willingness to instigate fighting to outweigh $c$'s willingness to deter fighting is
\[
  \textstyle \frac{\lambda p_{1s} + \alpha p_{2s}}{1-\de_p} - \frac{\de_p \alpha}{1-\de_p} (p_{1s}+p_{2s}) + \alpha \sum_{i=1}^{m-1} \de_p^i > \frac{\nu p_{1s} + \beta p_{2s}}{1-\de_c} - \frac{\de_c \beta}{1-\de_c} (p_{1s}+p_{2s}) + \beta \sum_{i=1}^{m-1} \de_c^i
\]

>>>>

Player $p$'s continuation value when the status quo is played for $m-1$ periods before ceding is $0 + \frac{\de^m}{1-\de} \alpha$, whereas the continuation value from war is $\frac{\lambda p_{1s} + \alpha p_{2s}}{1-\de} + \frac{\de}{1-\de}\alpha (1-p_{1s}-p_{2s})$. For player $c$, it is $0 + \frac{\de^m}{1-\de} \beta$ versus $\frac{\nu p_{1s} + \beta p_{2s}}{1-\de} + \frac{\de}{1-\de}\beta (1-p_{1s}-p_{2s})$. Thus the condition for $p$'s willingness to instigate fighting to outweigh $c$'s willingness to deter fighting is
\[
  \textstyle \frac{\lambda p_{1s} + \alpha p_{2s}}{1-\de} - \frac{\de \alpha}{1-\de} (p_{1s}+p_{2s}) + \alpha \sum_{i=1}^{m-1} \de^i > \frac{\nu p_{1s} + \beta p_{2s}}{1-\de} - \frac{\de \beta}{1-\de} (p_{1s}+p_{2s}) + \beta \sum_{i=1}^{m-1} \de^i
\]
